---
title: "Developing Data Product Week 4: Mortgage calculator"
author: "Jasmina"
date: "26 maj 2021"
output: ioslides_presentation
---

##The project overview

-The aim of this Assignment was to produce a simple Shiny app and a presentation.

-The Mortgage Calculator app is a simple app, that calculates your monthly mortgage payment.

- In order to calculate the monthly payment you need to:

    - input the loan amount (P)
    - adjust the slide bar to the right number of years (L)
    - and adjust the slide bar to the right annual interest rate (I)

##The calculation 
This is an example of the morgage calculation
```{r, echo=TRUE}
 morgage <- function(P, I, L){
        J <- I/(12*100)
        N <- 12*L
        M <- P*J/(1-(1+J)^(-N))
        return(M)
}
def_morgage <- morgage(10000, 6, 20)
```
The default estimated monthly payment is `r def_morgage`

##The ui code 
```{r, echo=TRUE, eval=FALSE}
shinyUI(fluidPage(
    
    # Application title
    titlePanel("Simple morgage calculator"),
    
    # Sidebar with  some inputs 
    sidebarLayout(
        sidebarPanel(
            #Input: Simple integer intervals
            numericInput("Principal", "What is your loan amount?", value = 10000),
            sliderInput("Years", "Length of loan in years", min = 0, max = 30, step = 1, value=20),
            sliderInput("Rate", "What is your interest rate in %?", min= 0, max = 50, step = 0.01, value = 6)
            #checkboxInput("ShowPlot", "Display plot?", TRUE)
        ),
        
        # Output the monthly payments 
        mainPanel(
            h2("Your estimated monthly payment:"),
            h1(textOutput("MonthlyPayment") )
            
        )
    )
))
```

##The server code
```{r, echo=TRUE, eval=FALSE}
shinyServer(function(input, output) {
    #Call to function morgage to calculate the monthly payment M   
    morgage <- function(P, I, L){
        J <- I/(12*100)
        N <- 12*L
        M <- P*J/(1-(1+J)^(-N))
        return(M)
        
    }
    
    
    output$MonthlyPayment <- renderText({ 
        morgage(P=input$Principal, I=input$Rate, L=input$Years)})
    
})
```